Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

\section{Observations}\label{sec:obs}
The data used in this study is from the Atmospheric Imaging Assembly
(AIA) \cite{2012SoPh..275...17L} on board the Solar Dynamics
Observatory (SDO) \cite{2012SoPh..275....3P}.  AIA observes in
multiple wavebands simultaneously and continuously, at high cadence
(12 seconds) and at high spatial resolution (0.6 arcseconds per pixel
at the Sun).  These data enable detailed comparisons between phenomena
seen in multiple wavebands, and are therefore ideal for assessing the
frequency content of the solar atmosphere.  The data was acquired
using the Lockheed Martin Solar Astrophysics cutout service
(http://lmsal.com/get\_aia\_data/).  Six hours of image data in the
time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
in the 171\AA and 193\AA\ wavebands is used.  These wavebands were
selected because previous studies in similar wavebands (TRACE 171\AA
and 193\AA) show the presence of coronal oscillations.  The cutout of
the Sun selected covers two adjacent $\beta\gamma$ regions NOAA AR
11575 and AR 11577.  This cutout was selected for two reasons.  First,
it is quiescent in that there were no X-ray flares or other
large-scale disturbances over the spatial extent of the cutout within
the time range.  Therefore, any variations in the plasma properties
cannot be ascribed to large-scale disturbances.  Second, the selected
cutout region contains a sunspot, and sunspots are known to be
locations over which three minute oscillations have been detected by
other instruments \citep{2002A&A...387L..13D}.

@@

>>>>

\section{Observations}\label{sec:obs}
The data used in this study is from AIA on board the Solar Dynamics
Observatory (SDO).  AIA observes images of the Sun in multiple
wavebands simultaneously and continuously, at high cadence (12
seconds) and at high spatial resolution (0.6 arcseconds per pixel at
the Sun).  These data enable detailed comparisons between phenomena
seen in multiple wavebands, and are therefore ideal for assessing the
frequency content of the solar atmosphere.  The data was acquired
using the Lockheed Martin Solar Astrophysics cutout service
(http://lmsal.com/get\_aia\_data/).  Six hours of image data in the
time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
in the 171\AA and 193\AA\ wavebands is used.  These wavebands were
selected because previous studies in similar wavebands (TRACE 171\AA
and 193\AA) show the presence of coronal oscillations.  The cutout of
the Sun selected covers two adjacent $\beta\gamma$ regions NOAA AR
11575 and AR 11577.  This cutout was selected for two reasons.  First,
it is quiescent in that there were no X-ray flares or other
large-scale disturbances over the spatial extent of the cutout within
the time range.  Therefore, any variations in the plasma properties
cannot be ascribed to large-scale disturbances.  Second, the selected
cutout region contains a sunspot, and sunspots are known to be
locations over which three minute oscillations have been detected by
other instruments \citep{2002A&A...387L..13D}.

@@

There is evidence that these power laws extend to much longer
frequencies than those considered here. \cite{2014AA...563A...8A}
integrate emission over small portions of active regions and the quiet
Sun as seen in the 19.5 nm passband image from the of the SOHO
\cite{1995SoPh..162....1D} Extreme ultraviolet Imaging Telescope (EIT;
\cite{1995SoPh..162..291D}) and show that the resulting time-series
has an approximate \PL\ \Fps.  The frequency range covered by their
study is approximately 0.01 - 1 mHz.
